The Driving Forces Behind API Evolution

### 2015-05-20 thesis/paper.tex
results rq1 intro

%Types intro
The results show that certain types of change are more prevalent than others, these results are shown in Table \ref{table:type_counts}. Analysis of the results showed that enhancive changes were the primary types of change that drive API evolution and that they act as a catalyst for many of the other changes in the API. Updative changes were found to be consequences of enhancive changes, rather than being drivers of evolution. Supporting the users of the API through the combination of preventive and groomative types of change, together formed another strong driver of API evolution. Reductive and adaptive changes, while important, did not strongly drive the evolution of the API. No evidence was found for corrective, performance types of change. Similarly, there was no evidence found for evaluative, consultive nor training activities.

@@

In the remainder of this section we will discuss the results related to each type of change category, discussing the results for each of them with examples from the changes identified between the two versions of the API. Subsequently, each of Lehman's laws will be discussed and our results will be presented showing if the laws apply to APIs or not.

%Re-write this intro a bit (since I moved it)
All of the identified changes have been given a type based the nature of the change according to the Types of Software Evolution and Software Maintenance decision tree \cite{chapin2001types}. Table \ref{table:type_counts} shows the total count of each type of change found in the different versions of the API.

Functionality is a prime driver of API evolution // Hardware is not a driving factor
Maintainability does not drive change // Documentation does not drive change
Standardising application development
Removing functionality

>>>>

%Types intro
The results show that certain types of change are more prevalent than others, these results are shown in Table \ref{table:type_counts}. Analysis of the results showed that enhancive changes were the primary types of change that drive API evolution and that they act as a catalyst for many of the other changes in the API. Updative changes were found to be consequences of enhancive changes, rather than being drivers of evolution. Supporting the users of the API through the combination of preventive and groomative types of change, together formed another strong driver of API evolution. Reductive and adaptive changes, while important, did not strongly drive the evolution of the API. No evidence was found for corrective or performance types of change. Similarly, there was no evidence found for evaluative, consultive or training activities.

@@

Following this section, we will discuss the results related to each type of change category, discussing the results for each of them with examples from the changes identified between the two versions of the API. Subsequently, each of Lehman's laws will be discussed and our results will be presented showing if the laws apply to APIs or not.
